---
title: "Getting started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
project_folder <- dirname(getwd())
path_to_env <- file.path(project_folder, ".env")
readRenviron(path_to_env)
api_base_url <- "https://restful-booker.herokuapp.com/"
auth_token <- Sys.getenv("AUTH_TOKEN")
headers <- list("Accept" = "application/json", "Content-type" = "application/json")
```

Let's instantiate the API client
```{r instance_booking_client}
booking_client <- httpeasyrest::HttpRestClient$new(
  base_url = api_base_url,
  headers = headers,
  token = auth_token
)
```

# Get all booking IDS as a DATAFRAME
```{r get_booking_ids_df}
api_data <- booking_client$get_dataframe(end_point = "booking")
head(api_data$http_resp)
```
# Get all bookings IDS as a JSON object
```{r get_booking_ids_json}
api_data <- booking_client$get_object(end_point = "booking")
head(api_data$http_resp)
```
# Get single specific booking record as JSON object
Notice that this specific API maps the `id` identifying the record in the URL itself, rather than as a query string
```{r get_single_booking_record}
booking_id <- api_data$http_resp[[1]]$bookingid
api_data <- booking_client$get_object(end_point = paste0("booking/", booking_id))
api_data$http_resp
```
# Create a single booking object afresh
Let's create a unique name that we can confidently search for it afterwards ensuring that is unique, and therefore its fetching is not down to luck - recall this API is used by many people.
```{r send_single_booking_record}
unique_name <- stringi::stri_rand_strings(1, 12)
data <- list(
  firstname = unique_name,
  lastname = "Jimenez",
  totalprice = 111,
  depositpaid = TRUE,
  bookingdates = list(
    checkin = "2018-01-01",
    checkout = "2019-01-01"
  ),
  additionalneeds = "Breakfast"
)
api_data <- booking_client$post_object(end_point = "booking", data)
testit::assert(isTRUE(api_data$success))
api_data$http_resp
```
Let's ensure that such object was indeed sent to the API successfully.
```{r send_single_booking_record_checkup}
end_point <- paste0("booking/", api_data$http_resp$bookingid)
inserted_booking <- booking_client$get_object(end_point = end_point)
testit::assert(inserted_booking$http_resp$firstname == unique_name)
inserted_booking$http_resp
```
# Delete a single booking object
Now we want to delete the same object we just inserted. Unfortunately the API does not allow deleting records, probably to avoid clashes among the multiple simultaneous users that may be calling the API. APIs usually accomplish that by returning an HTTP code = 403. You can know more about HTTP codes here https://cheatography.com/kstep/cheat-sheets/http-status-codes/.
```{r delete_single_booking_record, eval = FALSE}
end_point <- "booking/"
ret <- booking_client$delete_object(end_point = end_point, field = api_data$http_resp$bookingid)
testit::assert(ret$status_code == 403)
```
t::assert(isFALSE(deleted_booking$success))
```
