---
title: "Getting started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
project_folder <- dirname(getwd())
path_to_env <- file.path(project_folder, ".env")
readRenviron(path_to_env)
api_base_url <- "https://restful-booker.herokuapp.com/"
auth_token <- Sys.getenv("AUTH_TOKEN")
headers <- list("Accept" = "application/json", "Content-type" = "application/json")
```

Let's instantiate the API client
```{r instance_booking_client}
booking_client <- httpeasyrest::HttpRestClient$new(
  base_url = api_base_url,
  headers = headers,
  token = auth_token
)
```

# Get all booking IDS as a DATAFRAME
```{r get_booking_ids_df}
api_data <- booking_client$get_dataframe(end_point = "booking")
head(api_data$http_resp)
```
# Get all bookings IDS as a JSON object
```{r get_booking_ids_json}
api_data <- booking_client$get_object(end_point = "booking")
head(api_data$http_resp)
```
# Get single specific booking record as JSON object
Notice that this specific API maps the `id` identifying the record in the URL itself, rather than as a query string
```{r get_single_booking_record}
api_data <- booking_client$get_object(end_point = "booking/2657")
api_data$http_resp
```
# Create a single booking object afresh
Let's create a unique name that we can confidently search for it afterwards ensuring that is unique, and therefore its fetching is not down to luck - recall this API is used by many people.
```{r send_single_booking_record}
unique_name <- stringi::stri_rand_strings(1, 12)
data <- list(
  firstname = unique_name,
  lastname = "Jimenez",
  totalprice = 111,
  depositpaid = TRUE,
  bookingdates = list(
    checkin = "2018-01-01",
    checkout = "2019-01-01"
  ),
  additionalneeds = "Breakfast"
)
api_data <- booking_client$post_object(end_point = "booking", data)
testit::assert(isTRUE(api_data$success))
head(api_data$http_resp)
```
Let's ensure that such object was indeed sent to the API successfully.
```{r send_single_booking_record_checkup}
end_point <- paste0("booking/", api_data$http_resp$bookingid)
inserted_booking <- booking_client$get_object(end_point = end_point)
testit::assert(inserted_booking$http_resp$firstname == unique_name)
inserted_booking$http_resp
```
